---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aurrera

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/aurrera)](https://CRAN.R-project.org/package=aurrera)
[![R-CMD-check](https://github.com/turtletopia/aurrera/workflows/R-CMD-check/badge.svg)](https://github.com/turtletopia/aurrera/actions)
[![Codecov test coverage](https://codecov.io/gh/turtletopia/aurrera/branch/master/graph/badge.svg)](https://app.codecov.io/gh/turtletopia/aurrera?branch=master)
<!-- badges: end -->

The aurrera package makes adding a progress bar easy. Inspired by [tqdm Python package](https://github.com/tqdm/tqdm), a progress bar is just a single function call away. Wrap the object you iterate on with `aurrrera::pb()` and use it in most iterators like `lapply()`.

If you need a fine control over your progress bars, use [progressr package](https://github.com/HenrikBengtsson/progressr) instead.

## Installation

You can install the development version of aurrera from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("turtletopia/aurrera")
```

## User guide

Suppose we have some slowly processing function and a vector we want to apply this function to:

```{r initialize}
library(aurrera)

slow_paste <- function(...) {
  Sys.sleep(.2)
  paste(..., collapse = "")
}

x <- lapply(seq(3), function(i) sample(letters, 4))
```

This is the usual call you'd make:

```{r base_call}
lapply(x, slow_paste)
```

To add a progress bar, simply wrap `x` in `pb()`:

```{r base_bar}
lapply(pb(x), slow_paste)
```

These are some of the other iterators you can use aurrera with:

```{r other_iters}
sapply(pb(x), slow_paste)

purrr::map_chr(pb(x), slow_paste)

parallel::mclapply(pb(x), slow_paste)

plyr::llply(pb(x), slow_paste)

Reduce(slow_paste, pb(x))

purrr::reduce(pb(x), slow_paste)

library(foreach)
foreach::foreach(el = pb(x)) %do% slow_paste(el)
```

However, progress bars do not appear when using the old plain `for` loop... unless you make the iteration manually:

```{r for_loop}
x_pb <- pb(x)
v <- character()
for (i in seq_along(x_pb)) {
  # Pretend the operation below makes sense
  v <- c(slow_paste(x_pb[[i]]), v)
}
v
```

## Known bugs

- Progress bars do not appear when iterating within `for` loop, i.e. `for (el in pb(iterable))`. Use manual iteration instead (as presented above).

## End notes

I believe in equal rights and treatment for everybody, regardless of their sexuality, gender identity, skin tone, nationality, and other features beyond human control. Thus, I do not allow gglgbtq to be used in any project that promotes hate based on the aforementioned factors.
